\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemSkills}[2]{
  \item\normalsize{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemExperience}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubheadingEducation}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5}\\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingProject}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
    %   \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeSubItemSkills}[2]{\resumeItemSkills{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, label={}]}
\newcommand{\resumeSubHeadingListStartSkillsAwards}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
    \centerline{\textbf{\huge Tai Tran}}\vspace{0.15cm}
    \centerline{Email : \href{mailto:}{ti.taitran@gmail.com} $|$
    Mobile : 407-451-8515 $|$
    GitHub : \href{https://github.com/taiphlosion}{taiphlosion} $|$
    LinkedIn : \href{https://www.linkedin.com/in/ti-tai-tran/}{ti-tai-tran}}
% \end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Florida}{Gainesville, FL}
      {B.S in Computer Science; GPA: 3.24/4.00}{Jan 2022 -- Dec 2025}
    \resumeItemListStart
        \resumeItem{Relevant Coursework}
            {Data Structures and Algorithms, 
            Software Engineering, 
            Linear Algebra, 
            Discrete Mathematics, 
            Object-Oriented Programming, 
            Computer Organization,
            Multimodal Machine Learning,
            Operating Systems, 
            Programming Language Concepts
            }
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
% \section{Experience}
%   \resumeSubHeadingListStart
%     \resumeSubheading
%       {}{}
%       {}{}
%       \resumeItemListStart
%         \resumeItemExperience
%           {}
%         \resumeItemExperience
%           {}
%         \resumeItemExperience
%           {}
%         \resumeItemExperience
%           {}
%         \resumeItemListEnd
%     \resumeSubheading
%       {}{}
%       {}{}
%       \resumeItemListStart
%         \resumeItemExperience
%           {}
%         \resumeItemExperience
%           {}
%         \resumeItemExperience
%           {}
%         \resumeItemListEnd
%   \resumeSubHeadingListEnd

%-----------Projects-----------------
\section{Projects}
  \resumeSubHeadingListStart
    % \resumeSubHeadingListStart
        \resumeSubheadingProject
          {CaSMM (Online K-12 Education Website)}{Sep 2023 -- Dec 2023}
          \resumeItemListStart
            \resumeItemExperience
              {Help improve UI and implement new features for an eduational website for children through Agile methodology.}
            \resumeItemExperience
              {Utilized technologies such as React, Docker, PostgreSQL, Strapi to incorporate full-stack features.}
            \resumeItemExperience
              {Collaborated with teammates using Git, assigning issues, coordinating and participating in sprints as project manager ensuring timely delivery of updates.}
          \resumeItemListEnd
        \resumeSubheadingProject
          {Java Compiler}{Aug 2023 -- Nov 2023}
          \resumeItemListStart
            \resumeItemExperience
              {Collaborated with a partner through Git to develop a comprehensive Java-based compiler.}
            \resumeItemExperience
              {Fully implemented features such as lexical analysis, efficient parsing, semantic analysis, and code generation.}
            \resumeItemExperience
              {Optimized compiler performance and reliability through the creation of test cases and debugging.}
          \resumeItemListEnd
        \resumeSubheadingProject
          {Tech Lead, Lifestyle Alarm}{Dec 2023 -- Ongoing}
          \resumeItemListStart
            \resumeItemExperience
              {Collaborated with a development team to design and build an innovative alarm system application with Expo Go.}
            \resumeItemExperience
              {Implemented features like world clocks, calendar alerts, collaborative alarms, and integration with other platforms.}
            \resumeItemExperience
              {Lead management of the project’s GitHub repository along with other Tech Lead, ensuring effective version control.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
    
%-----------Activities-----------------
\section{Involvement}
    \resumeSubHeadingListStart
      \resumeSubheading
        {UF Club Quidditch/Quadball}{Gainesville, FL}
        {Treasurer}{Aug 2023 -- Apr 2024}
        \resumeItemListStart
          \resumeItemExperience
            {Oversee financial planning for current and future expenses, ensuring the club’s operational competitive needs are met.}
          \resumeItemExperience
            {Cooperated with UF Rec Sports on event collaboration, facility access, and boosting student engagement}
          \resumeItemExperience
            {Led fundraising initiatives to acquire more funds for future operations and actively recruit potential new members.}
        \resumeItemListEnd
        \resumeSubheading
        {UF SASE (Society of Asian Scientists and Engineers)}{Gainesville, FL}
        {Peer Mentor}{Aug 2023 -- Apr 2024}
        \resumeItemListStart
          \resumeItemExperience
            {Provide one-on-one guidance and support to underclassmen majoring in STEM adjust to university life.}
          \resumeItemExperience
            {Worked closely with other peer mentors and SASE officers to identify community needs and how to meet them.}
          \resumeItemExperience
            {Collaborated in the planning of community events and workshops promoting diversity and inclusion within STEM.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd
          
%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStartSkillsAwards
    \resumeSubItemSkills{Languages}{(Proficient) C++, Python, Java, JavaScript/TypeScript, HTML/CSS, MATLAB, \newline
    (Familiar) SQL, C, ARM Assembly}
    \resumeSubItemSkills{Tools}{Git, Jupyter Notebook, Docker, Strapi, React Native, PostgreSQL}
  \resumeSubHeadingListEnd

%-----------AWARDS-----------------
\section{Awards}
  \resumeSubHeadingListStartSkillsAwards
    \resumeSubItemSkills{University of Florida Dean's List}
      {College of Engineering (Summer - Fall 2023)}
    \resumeSubItemSkills{Machen Florida Opportunity Scholars}
      {Full grant and scholarship package awarded to First-Generation college students}
  \resumeSubHeadingListEnd

  \section{Activities \& Interests}
  \resumeSubHeadingListStartSkillsAwards
    \resumeSubItemSkills{Activities}
      {Open-Source Club, Club Quidditch/Quadball, Association for Computing Machinery (ACM), Society of Asian 
      Scientists and Engineers (SASE)}
    \resumeSubItemSkills{Interests}
      {Web/App Development, Competitive Programming, Open-Source Projects, AI and Machine Learning}
  \resumeSubHeadingListEnd
  
\end{document}
